A Switching Planner for Combined Task and Observation Planning

### 2010-11-26 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
I have to rush home now to let Katrina into the house. Will continue working on this tonight.
 - Charles

Finally, whether proceeding in a sequential or contingent session, our
continual planner maintains a factored representation of successive
{\em belief-states}, by performing belief revision according to
Eq~\ref{eq:revision}. Moreover, our internal representation of that
distribution corresponds more-or-less directly to an $(\pp{:init})$
declaration in DTPDDL. Our approach uses that underlying belief-state
as: (1) the source of determinisations for sequential planning, (2)
the basis for switching, and (3) the source for state abstraction in
contingent sessions.

@@

\Omit{
  Therefore, although our current implementation does not
  explicitly support it, our approach generalises to POMDPs with
  stochastic action models.
}

>>>>

Finally, whether proceeding in a sequential or contingent session, our
continual planner maintains a factored representation of successive
{\em belief-states}, by performing belief revision according to
Eq~\ref{eq:revision}. Moreover, our internal representation of that
distribution corresponds more-or-less directly to an $(\pp{:init})$
declaration in DTPDDL. Our approach uses that underlying belief-state
as: (1) the source of determinisations for sequential planning, (2)
the basis for switching, and (3) a mechanism to guide construction of
an abstract process for contingent sessions.

@@

%% \Omit{
%%   Therefore, although our current implementation does not
%%   explicitly support it, our approach generalises to POMDPs with
%%   stochastic action models.
%% }
